Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-06 manuscript.tex
5.3 updates

%-----------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Detection limits when using the RV derived with the Normal or the Skew Normal density} \label{sec:detect_limits}

In the preceding section, we saw that the RV measured when considering a SN or a Normal density present different amplitudes, mainly in the case of SN mean RV. However, when correcting for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, it seems that we are able to reach the same RV precision. In this section, we want to investigate if for some of the three different RV definitions presented in this paper, it is easier or more difficult to detect planetary signals when considering stellar activity. To do so, we estimated what would be the minimum amplitude of a planetray signal we could detect at different orbital periods when considering data affected by stellar activity.

>>>>

%-----------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Detection limits when using the estimated RVs from the Normal or the Skew Normal models} \label{sec:detect_limits}

In the preceding section, we saw that the estimated RV measured when considering a SN or a Normal model resulted in different amplitudes, especially when using the SN mean RV. However, when correcting for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, it seems same RV precision is achieved.  \jessi{It would be good to be a little more precise in the previous sentence:  by ``same precision'' do you mean the same std of the residuals?  Given the first sentence the reader may be confused because it says they have different amplitudes estimated.}
In this section, we investigate the ability of the three different RV estimators' (N mean RV, SN mean RV, and SN median RV) ability to detect planetary signals among stellar activity.
To carryout this test, the minimum detected amplitude of a planetary signal is estimated at different orbital periods when considering data affected by stellar activity.
